Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-27 paper/ms.tex
in the middle of the Results section

\section{Results}

\begin{figure}
\begin{center}
\includegraphics[width=1.10\linewidth,angle=0]{./plots/Fig1.pdf}
\caption{ \label{figure:laes_dist} Surface density of dark
  matter halos as a function of a minimum halo mass to count the
  total number of elements in a volume. Each line represents on of the
  $210$ volumes of dimensions $46\times 35\times 41$ h${-3}$Mpc$^{3}$
  in the Bolshoi simulation. The horizontal grey band represents the
  range of surface densities observed for LAEs at $z=3.1$ as reported
  by \citep{Yamada2012}.}
\end{center} 
\end{figure}

\subsection{Dark Matter Halo Number Density}
In Figure \ref{fig:laes_dist} we present the results for  the
integrated dark matter halo surface density as a function of halos
mass. Each line corresponds to one of the 210 sub-volumes in the
Bolshoi simulation. The shadowed area indicates the surface density
values for LAEs allowed by the observations.

This result allows us to better understand the expected trends for the
LAEs' preferred mass and the occupation fraction.  From this Figure we
can read which models do not have achance reproduce the
observations. Regions in the plot where the halo surface density
values are below the observational constraint correspond to high
masses halo masses. For a LAE model ${\mathcal M}$ with a minimum mass
$M_{\rm   min}> 3 \times 10^{11}$\hMsun located inthat mass range, the
surface density is too low compared with observations.

@@

\subsection{Kolmogorov-Smirnov Tests}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}
\vspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}\\
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
  $P>0.05$ in the three different of grouping the mock fields. In the
  case of the {\tt match} and {\tt random} methods the  color code
  corresponds to the number of mock surveys that are found to
  be compatible with observations. For the {\tt full} method the
  colour code corresponds to the results of $100$ times the maximum $P$ value
  resulting from the KS test. \label{figure:landscape}.}  
\end{figure*}

Figure \label{figure:landscape} presents the regions in the parameter
space $M_{\rm min}$-$M_{\rm max}$ where the KS test yields values of
$P>0.05$. We consider that for those models it is not possible to rule out the null
hypothesis, namely that the number density in simulated data and the observations come
from the same parent distribution. Each panel corresponds to the three different ways of
grouping the mock fields. In the case of the methods {\tt{Match}}
and {\tt{Random}} the color code indicates the fraction of these 15
mock surveys with with $P>0.1$. The third panel shows the result for
the method {\tt{Full}}, in this case the color code correspond
to the value maximum value of $100\times P$ for a model with those
mass ranges.

These results clearly distinguish three mass regimes. In the first regime, at
high mass values, we find that LAE models with minimum mass of $M_{\rm
  min}>10^{11.5}$\hMsun are not compatible with observations. There is
a second regime for masses below $M_{\rm
  min}=3\times 10^{10}$ any values for $M_{\rm min}$ and $M_{\rm max}$
can be made compatible with observations, provided that
$f_{\rm occ}$ is fine tuned to do it. In an intermediate mass regime,
for minimum mass values $3\times 10^{10}\hMsun < M_{\rm min}< 3\times 10^{11}\hMsun$ only a
limited range of models with $M_{\rm max}$ with occupation fraction
$f_{\rm occ}\sim 1$ is able to reproduce observations.

In these three different mass regimes the occupation monotonically
decreases as a function of the minimum halo mass $M_{\rm min}$. In
Figure XXX we show this treend in three panels following the same
correspondence as Figure XXX. From these results we interpret that the
different mass regimes that were identified correspond to best fit
models with $f_{\rm occ}\sim 1$, $0<f_{\rm occ}<1$ and $f_{\rm
  occ}\sim 0$, respectively.

The two {\tt match} and {\tt random} methods present the highest
number of matching mock surveys in the medium mass regime. However, it
is important to keep in mind that not all the mock surveys for a
sucessful model ${\mathrm M}$ present a high value $P>0.1$, only a
modest fraction seems to be consistent with observations. This shows that the
cosmic variance is still present on the physical scales probed by
observations. This will be considered in more detail in the discussion
seccion.

To illustrate this point, in Figure \ref{fig:mocks} we present the
results for two mock fields for the {\tt{Match}} method for a model
with the same parameters, but two extreme values for the KS test.

Conversely there are different models where the KS test yield values of
$P\sim 1$. To illustrate the kind of success represented by these
models, we have selected these best ones in the case of the method
{\tt{MatchObs}}. Figure XXX shows in the main panel the spatial
distribution of the mock surveys, the smaller panel shows the
corresponding surface density distribution and the observational
constraint.

In what follows we will focus our discussion on the mocks constructed
with the {\tt{Match}} and {\tt{Random}} methods.

@@

>>>>

\section{Basic Results}

\begin{figure}
\begin{center}
\includegraphics[width=1.10\linewidth,angle=0]{./plots/Fig1.pdf}
\caption{ \label{fig:laes_dist} Surface density of dark
  matter halos as a function of a minimum halo mass to count the
  total number of elements in a volume. Each line represents on of the
  $210$ volumes of dimensions $46\times 35\times 41$ h${-3}$Mpc$^{3}$
  in the Bolshoi simulation. The horizontal grey band represents the
  range of surface densities observed for LAEs at $z=3.1$ as reported
  by \citep{Yamada2012}.}
\end{center} 
\end{figure}

\subsection{Dark Matter Halo Number Density}

In Figure \ref{fig:laes_dist} we present the results for  the
integrated dark matter halo surface density as a function of halo
mass. Each line corresponds to one of the 210 sub-volumes in the
Bolshoi simulation. The gray band indicates the surface density
values for LAEs allowed reported in observations \citep{Yamada2012}.

This result provides the basis to understand why a range of models
${\mathcal M}$ can be expected to be consistent with
observations. In Figure \ref{fig:laes_dist} we can read that models
with a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
surface number density lower than the observational
constrain. The oppossite is true in models with $\log_{10} M_{\rm min}<10.5$
that will show surface number density larger than observations, this
implies that in such models the occupation fraction has to be tuned
$f_{\rm occ}<1.0$ as to lower the halo numeber density to match the
gray band values.

%This basic result provides the basis to understand the range of models
%${\mathcal M}$ expected trends for the
%LAEs' preferred mass and the occupation fraction.  
%From this Figure we
%can read which models do not have achance reproduce the
%observations. Regions in the plot where the halo surface density
%values are below the observational constraint correspond to high
%masses halo masses. For a LAE model ${\mathcal M}$ with a minimum mass
%$M_{\rm   min}> 3 \times 10^{11}$\hMsun located inthat mass range, the
%surface density is too low compared with observations.

@@

In the next subsection we quantify this intuition by means of the KS
tests between mock surveys and observations.

\subsection{Three Regions in Parameter Space}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}
\vspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}\\
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
    min}-f_{\rm occ}$ (right) planes for all models with
  $P>0.05$ in two different ways used to construct the mock
  surveys. The color code corresponds to the number of mock surveys
  that are found to be compatible with observations in terms of the KS
  test with $P>0.05$. Only regions of parameter space with at least
  one (1) consistent mock survey are included. \label{fig:landscape}}   
\end{figure*}

Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
min}-M_{\rm max}$, $M_{\rm min}-f_{\rm occ}$ where the KS test yields
values of $P>0.05$ at least for one mock survey. For those models it
is not possible reject the hypothesis that the simulated and observed
data for the surface number density come from the same parent
distribution.

The upper (lower) panels correspond to the {\texttt match} ({\texttt
  random}) method to build the mock surveys from individual
fields. The color code shows the number of mock surveys consistent
with observations. In both cases there are three regions of parameter
space that can be clearly distinguised.

The first region corresponds to models where the minimum mass is high
$\log_{10}M_{\rm min}> 11.5$. None of this models is compatible with
observations as expected from the results in the previous section. For
these models the number density of LAEs is too low.

The second region corresponds to an intermediate range for the minimum
mass $10.5<\log_{10}M_{\rm min}<11.5$ where regardless of the value of
the maximum mass $M_{\rm max}$ it is possible to tune the occupation
fraction $f_{\rm occ}$ to bring some of the mock observations into
good agreement with observations. In this region in parameter space
one can thus find two extreme kinds of models.  One kind where the
mass interval is very narrow with sizes smaller than $<0.3$ dex (a
factor of two in mass) and others where the mass interval is very
extended, larger than $1.0$ dex, going up to the maximum halo mass
present in the simulation at that redshift.

The third region in parameter space corresponds to $\log_{10}M_{\rm
  min}<10.5$. In this case only models with a narrow mass interval of
at most $0.5$ dex ($\log_{10}M_{\rm max}<11.0$) and low
occupation fractions $f_{\rm occ}<0.3$ are allowed.

%Figure \label{figure:landscape} presents the regions in the parameter
%space $M_{\rm min}$-$M_{\rm max}$ where the KS test yields values of
%$P>0.05$. We consider that for those models it is not possible to rule out the null
%hypothesis, namely that the number density in simulated data and the observations come
%from the same parent distribution. Each panel corresponds to the three different ways of
%grouping the mock fields. In the case of the methods {\tt{Match}}
%and {\tt{Random}} the color code indicates the fraction of these 15
%mock surveys with with $P>0.1$. The third panel shows the result for
%the method {\tt{Full}}, in this case the color code correspond
%to the value maximum value of $100\times P$ for a model with those
%mass ranges.

%These results clearly distinguish three mass regimes. In the first regime, at
%high mass values, we find that LAE models with minimum mass of $M_{\rm
%  min}>10^{11.5}$\hMsun are not compatible with observations. There is
%a second regime for masses below $M_{\rm
%  min}=3\times 10^{10}$ any values for $M_{\rm min}$ and $M_{\rm max}$
%can be made compatible with observations, provided that
%$f_{\rm occ}$ is fine tuned to do it. In an intermediate mass regime,
%for minimum mass values $3\times 10^{10}\hMsun < M_{\rm min}< 3\times 10^{11}\hMsun$ only a
%limited range of models with $M_{\rm max}$ with occupation fraction
%$f_{\rm occ}\sim 1$ is able to reproduce observations.

%In these three different mass regimes the occupation monotonically
%decreases as a function of the minimum halo mass $M_{\rm min}$. In
%Figure XXX we show this treend in three panels following the same
%correspondence as Figure XXX. From these results we interpret that the
%different mass regimes that were identified correspond to best fit
%models with $f_{\rm occ}\sim 1$, $0<f_{\rm occ}<1$ and $f_{\rm
%  occ}\sim 0$, respectively.

%The two {\tt match} and {\tt random} methods present the highest
%number of matching mock surveys in the medium mass regime. However, it
%is important to keep in mind that not all the mock surveys for a
%sucessful model ${\mathrm M}$ present a high value $P>0.1$, only a
%modest fraction seems to be consistent with observations. This shows that the
%cosmic variance is still present on the physical scales probed by
%observations. This will be considered in more detail in the discussion
%seccion.

%To illustrate this point, in Figure \ref{fig:mocks} we present the
%results for two mock fields for the {\tt{Match}} method for a model
%with the same parameters, but two extreme values for the KS test.

%Conversely there are different models where the KS test yield values of
%$P\sim 1$. To illustrate the kind of success represented by these
%models, we have selected these best ones in the case of the method
%{\tt{MatchObs}}. Figure XXX shows in the main panel the spatial
%distribution of the mock surveys, the smaller panel shows the
%corresponding surface density distribution and the observational
%constraint.

%In what follows we will focus our discussion on the mocks constructed
%with the {\tt{Match}} and {\tt{Random}} methods.

@@

... Discuss all this in terms of the star formation efficiency in
Behroozi et al.
